# Installation {#installation}

In order to use the discoveryengine, you'll have to install it. And in order to successfully install the discoveryengine, you'll have to install a few other packages, too. The [introduction to RStudio video](#r-intro) showed you how to install new packages both by typing install commands into the console, or by using RStudio's "Packages" pane. Here, we'll go through the installation step-by-step by typing out the install commands (copying and pasting is a good way to avoid frustrating typos!).

Note that installation can sometimes be a pain. But once you've gotten through the process successfully, you won't have to deal with it again! 

## Required packages

At this point, you should have already: 

- tested your CDW connection
- installed `getcdw`
- run a test query

If you haven't completed all of those items, head over to [the step-by-step guide](#test-cdw) and complete those steps, and then return here.

Ok, so if you've got `getcdw` working properly, that means you've already installed `devtools`. All that's left is to install `listbuilder` and `discoveryengine` packages:

```{r install_disco, eval = FALSE}
devtools::install_github("tarakc02/listbuilder")
devtools::install_github("tarakc02/discoveryengine")
```

There are a couple more packages that are optional, but will make the discoveryengine even better:

```{r install_disco_optional, eval = FALSE}
devtools::install_github("tarakc02/preprocessr")
install.packages("DT")
```

## A disco test

In order to make sure everything is working properly, we'll run a quick disco test:

```{r disco_test, cache = TRUE}
# you'll always load the discoveryengine package before doing anythying else
library(discoveryengine)

# make sure we can create a disco definition
high_cap = has_capacity(1)

# make sure that things print properly
high_cap

# make sure we can send the defintion to the data warehouse
display(high_cap)
```

If you got this far without any problems, then congrats! You are a disco dancer!
