# Installation {#installation}

Discoveryengine (and all packages we use in Prospect Developmemt) is installed on the R drive. The most important step to make sure you can access these packages is to set up your default library path to the shared packages repository.

Run a quick test to see your current library path:

```{r library_path, eval = FALSE}
.libPaths()
```

The first result returned shoud be "R:/Prospect Development/Prospect Analysis/pd-shared-r-packages". If it's not, follow the steps below to change your default library path.

Step 1: Open a new RStudio session and run the following script:

```{r set_up_renviron, eval = FALSE}
# the first part sets up the new package directory
package_dir <- "R:/Prospect Development/Prospect Analysis/pd-shared-r-packages"
if (!dir.exists(package_dir)) dir.create(package_dir, recursive = TRUE)

# then make a configuration file that notifies R of the new package directory
# change [username] to your actual username in your P drive - usually LastNameFirstInitial
env_file <- "P:/[username]/.Renviron"
if (!file.exists(env_file)) file.create(env_file)

# and add the new location to the configuration file
cat("\nR_LIBS_USER='", package_dir, "'", 
    sep = "", file = env_file, append = TRUE)
```

Step 2:

Find the newly created .Renviron file. It will be in your P drive. 

Step 3: 

Move the .Renviron file to your Documents folder. This should be located in D:\\Users\\[username]\\Documents. Simply drag and drop.

Step 4:

Quit your current RStudio session and open a new one. Try running the following test again:

```{r library_path2, eval = FALSE}
.libPaths()
```

If the PD shared packages depository is returned, you are ready to start using Disco Engine. If not, contact the Analytics Team to troubleshoot your situation.

## Before you continue

At this point, you should have already: 
- tested your CDW connection
- installed `getcdw`
- run a test query

If you haven't completed all of those items, head over to section [Test CDW](#test-cdw) and complete those steps, and then return here.

## A disco test

In order to make sure everything is working properly, we'll run a quick disco test:

```{r disco_test}
# you'll always load the discoveryengine package before doing anythying else
library(discoveryengine)
# make sure we can create a disco definition
high_cap = has_capacity(1)
# make sure that things print properly
high_cap
# make sure we can send the defintion to the data warehouse
display(high_cap)
```

If you got this far without any problems, then congrats! You are a disco dancer!
