# (PART) Examples {-}

# Political economy list {#ex-political-economy}

Here's the request:

>Can you please generate a prospect list for me that includes econ, political economy, poli sci and business grads. And also include donors to Haas Center, Goldman School and CEGA? 

I start with the part I already know -- business grads.

```{r, kassie-ex1}
library(discoveryengine)
is_business_grad = has_degree_from(business)
```

I believe Economics, Political Economy, and Political Science are all majors. I don't know major codes, but most widgets have a built-in lookup feature:

```{r, kassie-ex2}
majored_in(?econ)
```

Ok, looks like `economics` and `political_economy` should definitely be included. What about political science?

```{r, kassie-ex3}
majored_in(?political)
```

So now I have what I need for the other graduates:

```{r, kassie-ex4}
is_poli_econ_grad = majored_in(political_science, political_economy, economics)
```

Now I need to find donors to the Haas Center, Goldman School, and CEGA. Some follow-up clarified that the "Haas Center" here is referring to the [Haas Institute for a fair and inclusive society](http://haasinstitute.berkeley.edu/) . I don't know if that is an area of giving, a department, a fund? So I use the brainstorm bot:

```{r, kassie-ex5, cache = TRUE}
brainstorm_bot("haas inst")
```

Ah ha! It's the department.

```{r, kassie-ex6}
is_haas_ctr_donor = gave_to_department(HDRC)
```

CEGA is the "effective global action center." Once again, I'll ask the brainstorm bot for suggestions:

```{r, kassie-ex7, cache = TRUE}
brainstorm_bot("global action")
is_cega_donor = gave_to_department(CEGA)
```

I already happen to know that the Goldman School is an area of giving, so:

```{r, kassie-ex8}
is_goldman_donor = gave_to_area(public_policy)
```

The request was for people who meet any of the given criteria, so I'll use  `%or%` to combine them:

```{r, kassie-ex9, cache = TRUE}
prospect_list = is_business_grad %or% 
    is_poli_econ_grad %or%
    is_haas_ctr_donor %or%
    is_cega_donor %or%
    is_goldman_donor

display(prospect_list)
```

