# LYBUNTs {#ex-lybunt}

```{r ex-lybunt-loadlib}
# i always begin by loading the disco engine if it isn't already loaded
library(discoveryengine)
```

Anyone involved in an annual solicitation cycle will have some interest in the population referred to as *LYBUNT*, which stands for **L**ast **Y**ear **Bu**t **N**ot **T**his Year. That is, someone who gave last year but has not given this year. How can we create such a definition in the Disco Engine?

To make the example concrete, let's say we're identifying LYBUNTs for the school of Social Welfare. What I'd like to get to is:

```{r ex-lybunt-strat, eval = FALSE}
LYBUNT = last_year %but_not% this_year
```

So, all I really need to do is define `last_year` and `this_year`. I'm writing this example in September, 2016, so I'll define "last year" as FY2015-16, or in other words, July 1, 2015 - June 30, 2016:

```{r ex-lybunt-last-year}
last_year = gave_to_area(social_welfare, from = 20150701, to = 20160630)
```

And now for this year. Since the `to` argument is optional, I can just do:

```{r ex-lybunt-this-year}
this_year = gave_to_area(social_welfare, from = 20160701)
```

Now I can create my `LYBUNT` definition, as I strategized above:

```{r ex-lybunt-lybunt, cache = TRUE}
LYBUNT = last_year %but_not% this_year
display(LYBUNT)
```

Finally, recall that [every widget has a default](#use-defaults) set up if you don't enter any codes. Looking at `?gave_to_area` I can see that if I don't use an area of giving codes, I just get any giving anywhere. I can use this knowledge to get campus-wide LYBUNTs:

```{r ex-lybunt-campuswide, cache = TRUE}
last_year = gave_to_area(from = 20150701, to = 20160630)
this_year = gave_to_area(from = 20160701)
LYBUNT = last_year %but_not% this_year
display(LYBUNT)
```
