# Donors who aren't degreeholders {#ex-sim-donors}

```{r ex-sim-donors-loadlib, message = FALSE}
# i always begin by loading the disco engine if it isn't already loaded
library(discoveryengine)
```

We have what looks like an easy request:

> Find donors to the School of Information who are not SIM degree holders.

Having already looked up the codes, you immediately think: 

```{r eval = FALSE}
gave_to_area(SIM) %but_not% has_degree_from(LI)
```

Unfortunately, as you begin reviewing the results, you notice that you produced a list that includes spouses of degree holders who received credit for household gifts to SIM. 

What we actually want here is not "donors who are not degreeholders" but rather "donor households that are not degree-holding households." Here "donor households" has the standard meaning, and "degree-holding household" means a household where at least one of the spouses has a degree.

So instead:

```{r}
non_alum_donors = 
    household(gave_to_area(SIM)) %but_not%
    household(has_degree_from(LI))
```

To make it even more clear what it is we're doing with this definition, it helps to re-write it with more descriptive names:

```{r}
is_donor_hh = household(gave_to_area(SIM))
is_degree_hh = household(has_degree_from(LI))

non_alum_donor_hh = is_donor_hh %but_not% is_degree_hh
```

## Why it works

By householding each component of the definition before combining them with `%but_not%`, I am making the household the basic unit of analysis, rather than the individual. This often becomes necessary when we're working with giving or portfolios (which we usually treat as characteristics of a household) and we want to exclude characteristics such as degree or student activity (which are characteristics of an individual). 
