# Cheat Sheet {#cheat-sheet}

## Getting started

* Always start a session with `library(discoveryengine)`

```{r cheat-sheet-loadlib}
library(discoveryengine)
```

* Not sure where to begin? Use `show_widgets()` to view a searchable and sortable list of available widgets. For more tips on finding widgets, check out [the section on finding widgets](#working-with-finding-widgets).
* Still not sure what to do? Try using the [brainstorm bot](#brainstorm-bot). For instance if you are looking for people who played on the basketball team, type `brainstorm_bot("basketball")`
* Multiple widgets can be combined using the operators `%and%`, `%or%`, or `%but_not%`. For example, `gave_to_area(natural_resources) %but_not% in_unit_portfolio(natural_resources)`

## Knowing about defaults
Be aware of defaults: If you're ever wondering about any of the default settings for a widget, utilize the built-in documentation to learn more. For example: `?has_affiliation` shows me that the option `include_former` defaults to `TRUE`, meaning that the `has_affiliation` widget will automatically include former (in addition to current) affiliations, unless you add `include_former = FALSE`. 

An incomplete list of widget options and their default settings:

* `has_degree_from` and `majored_in`: By default, these include undergraduate and graduate degreeholders, and exclude attendees.
* `attended_event`: By default, non-attendees (coded as "invited but did not attend") are excluded, but can be included with `include_non_attendees = TRUE`
* `has_affiliation`, `has_interest`, and all of the employment-based widgets have an `include_former` option that defaults to `TRUE`
* `in_unit_portfolio` has an option to `include_inactive` that defaults to `FALSE` (by default, only the active proposal assignments are considered)

The best way to find out options, defaults and other information about widgets is to use the built-in documentation.

## Output

Use `display` for output. Recall that you can use the equals sign `=` to assign names to your disco engine definitions, to make it easier to refer to them when `display`ing or doing other operations:

```{r cheat-sheet-output-1}
basketball_player = played_sport(basketball_men, basketball_women)
display(basketball_player)
```

If instead of just viewing IDs on the screen, you'd like to export them (perhaps to use in a CADS savedlist), just add a filename: `display(basketball_player, file = "basketball-players")` and a file called "basketball-players.csv" will appear in your working directory. *Note that the exported file has a header, so when you upload it to an Advance savedlist, make sure to check the "First row is a header" box.*

## Code lookup

Most widgets rely on the coding found in CADS for their input, but you probably haven't memorized all of the codes! By using a question-mark inside of a widget, you can do look-ups on the fly:

```{r cheat-sheet-lookup}
gave_to_department(?band)
```

Codes (such as `CALBAND`) and synonyms (such as `cal_band`) can be used interchangeably, so use whichever feels more comfortable. 

## The best widgets for . . .

The following may be incomplete and is *not* a substitute for using `show_widgets()`, but may come in handy in a pinch. Find out more about any one of these by using the built-in help. For example, to learn more about the `gave_to_area` widget, type `?gave_to_area`

* Giving widgets: `gave_to_area`, `gave_to_department`, `gave_to_fund`
* Ratings: `has_capacity`, `has_implied_capacity`, `has_major_gift_score`, `has_gift_planning_score`
* Academic and student experience: `has_degree_from`, `majored_in`, `participated_in`, `played_sport`, `received_award`
* UCB affiliations: `has_affiliation`, `on_committee`, `received_award`
* Interests, etc: `has_interest`, `has_philanthropic_affinity`
* Employment: `works_in_industry`, `has_occupation`, `has_position`, `job_title_like`
* Geography: `lives_in_county`, `lives_in_msa`, `lives_in_zip`, `lives_near`, `works_in_county`, `works_in_msa`, `works_in_zip`, `works_near`

## Text search

Though most widgets rely on codes from CADS as inputs, some are search-based. Just like the `brainstorm_bot`, which is also based on text search, these widgets require you to use quotation marks around the search term(s). Here are some examples:

* `contact_text_contains("neuro*", "brain")`
* `fund_text_contains("diversity")`
* `research_miner("underrepresented")`

**Note:** The `brainstorm_bot` will help you find things through the code tables, but it will not do big text searches of things like contact reports, fund biographies/terms, and research profiles. For that kind of specialized search, you should use these text search based widgets.

## Other

Type `show_suspect_pools()` to view a list of all Suspect Pools, which is useful in conjunction with the `in_suspect_pool` widget.